---
title: "Child Age/Weight dependency"
subtitle: "The WHO Child Growth Standards"
author: "Achim Gerhardt"
date: "5 Januar 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

source("plotFunction.R")
```

## The WHO Child Growth Standards
The idea of this app is to visualize WHO child growth standards data. For this project we focus on the age/weigth data for boys and girls.

These standards were developed using data collected in the WHO Multicentre Growth Reference Study.

## The Data
The data contains the percentiles of the weight by age of the child. Interactive example plot using the same function as the app for 30 day old girls:

```{r}

percentiles_girls <- subset(read.table("data/wfa_girls_p_exp.txt", header = TRUE, sep="\t", stringsAsFactors = FALSE), select = c(Age, P3, P10, P15, P50, P85, P90, P97))[1:40,]

plotPercentiles(percentiles_girls, 30, nrow(percentiles_girls))
```


## App
The app is splited in three parts. 

* _server.R_ loads the data and contains the business logic 
* _ui.R_ describes the user interface 
* _prepare_data.R_ is responsible for downloading and preprocessing (extracting) the data from the WHO page. This part is only necessary if you want to redownload the data.

## Links
### App
The app: https://acger.shinyapps.io/week4/  

The code: https://github.com/acger/developing-data-products/tree/gh-pages/week4  

### Data from WHO
https://www.who.int/childgrowth/standards/en/
